Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-23 mu/article/article.tex
sab

response than the $\mathrm{yz}$ and for the same incoming beam energy the components have values of

@@

We found that for both cases the components have similar contributions for the corresponding response and for
an incoming energy beam of 1.934\,eV  we have the first local maximum resulting
in a value of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|= 6.6$\,Km/s along the
$x$ direction  with polar and azimuthal spin polarization angles

@@

$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ being the spin
directed over the first Cartesian Quadrant of the $xy$ plane.

>>>>

response than the $\mathrm{yz}$ and for the same incoming beam energy the
components have values of

@@

We found that for both cases the components have similar contributions for the
corresponding response and for an incoming energy beam of 1.934\,eV  we have the
first local maximum resulting in a value of
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|= 6.6$\,Km/s along the $x$ direction
with polar and azimuthal spin polarization angles

@@

$\varphi_{\mathrm{x}}(\omega,\alpha)=59^{\circ}$ being the spin directed over
